MAESTROeX: A Massively Parallel Low Mach Number Astrophysical Solver

### 2019-02-11 MAESTROeX_I/paper.tex
small updates

\title{MAESTROeX}

@@

\author{Doreen Fan}
\affil{Lawrence Berkelely National Laboratory \\
Center for Computational Sciences and Engineering \\
One Cyclotron Road, MS 50A-3111 \\
Berkeley, CA 94720, USA}

\author{Andrew Nonaka}
\affil{Lawrence Berkelely National Laboratory \\
Center for Computational Sciences and Engineering \\
One Cyclotron Road, MS 50A-3111 \\
Berkeley, CA 94720, USA}

\author{Ann Almgren}
\affil{Lawrence Berkelely National Laboratory \\
Center for Computational Sciences and Engineering \\
One Cyclotron Road, MS 50A-3111 \\
Berkeley, CA 94720, USA}

@@

%% Mark off the abstract in the ``abstract'' environment.
\begin{abstract}
We present MAESTROeX, a next-generation solver for low Mach number astrophysical flows.
Here we summarize implementation details as well new spatiotemporal integration schemes
developed for increased accuracy and a simpler base state treatment.  The code is written
in the AMReX software framework for massively parallel block-structured adaptive mesh
refinement applications.

\end{abstract}

@@

Many astrophysical flows are highly subsonic; sound waves carry sufficiently little energy that they do not significantly affect the convective dynamics of the system.
In many of these flows, long-time convective dynamics are of interest.
Thus, using a traditional compressible astrophysical solver is highly inefficient.
One approach to this problem is to use low Mach number hydrodynamic models.

@@

\section{Performance and Scaling}

show OpenMP performance, maybe some comparisons with old Maestro?

@@

future stuff: rotation, SDC, high-order, GPUs

@@

>>>>

\title{MAESTROeX: A Massively Parallel Low Mach Number Astrophysical Solver}

@@

\author[0000-0002-3246-4315]{Duoming Fan}
\affil{Lawrence Berkelely National Laboratory \\
Center for Computational Sciences and Engineering \\
One Cyclotron Road, MS 50A-3111 \\
Berkeley, CA 94720, USA}

\author[0000-0003-1791-0265]{Andrew Nonaka}
\affil{Lawrence Berkelely National Laboratory \\
Center for Computational Sciences and Engineering \\
One Cyclotron Road, MS 50A-3111 \\
Berkeley, CA 94720, USA}

\author[0000-0003-2103-312X]{Ann S. Almgren}
\affil{Lawrence Berkelely National Laboratory \\
Center for Computational Sciences and Engineering \\
One Cyclotron Road, MS 50A-3111 \\
Berkeley, CA 94720, USA}

@@

%% Mark off the abstract in the ``abstract'' environment.
\begin{abstract}
We present MAESTROeX, a massively parallel solver for low Mach number astrophysical flows.
This new solver leverages the algorithmic capabilities of the previous MAESTRO code
while taking advantage of the next-generation AMReX software framework block-structured
adaptive mesh refinement applications.
Using our previous studies on white dwarf convection as a benchmark, we characterize
the performance of our new code.
We have also developed new temporal integration schemes that have a much simpler treatment
of the base state, while allowing for more straightforward extensions to state-of-the
art, high-order multiphysics coupling schemes.
Also, we present an improved spatial coupling scheme between the hydrostatic base
state and the Cartesian grid full-state.
\end{abstract}

@@

Many astrophysical flows are highly subsonic; 
sound waves carry sufficiently little energy that they do not significantly affect the convective dynamics of the system.
In many of these flows, long-time convective dynamics are of interest.
Thus, using a traditional compressible astrophysical solver is highly inefficient.
One approach to this problem is to use low Mach number hydrodynamic models.
In a low Mach number approach, sound waves are eliminated from the governing equations by requiring that the
thermodynamic variables evolve subject to a specified ambient pressure that varies only as a function of altitude and time.
In the low Mach equations, the equation of state is recast as a divergence constraint on velocity, requiring an
elliptic solve for pressure in the spirit of projection methods for incompressible flow.

@@

\subsection{Scaling}
Scaling with OpenMP

\subsection{Performance Compared to Original MAESTRO}
Compare to original MAESTRO

\section{Test Problems}
white dwarf convection runs with 3 algorithms (original, new temporal, new temporal + irregular base state)

@@

science: rotation, solar physics, MHD
algorithm: SDC, high-order
implementation: GPUs

@@

This work was supported by SciDAC... (contract number)

This research used resources of the National Energy Research Scientific Computing Center (NERSC), a U.S. Department of Energy Office of Science User Facility operated under Contract No. DE-AC02-05CH11231.
